\documentclass{resume}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.35in,top=0.20in,right=0.35in,bottom=0.15in]{geometry}
\usepackage{setspace}
\setstretch{0.92}
\emergencystretch=2em
\usepackage{enumitem}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% Redefine section and name spacing for single-page layout
\renewcommand{\sectionskip}{\vspace{2.5pt}}
\renewcommand{\sectionlineskip}{\vspace{1pt}}
\renewcommand{\nameskip}{\vspace{1pt}}
\renewcommand{\addressskip}{\vspace{1pt}}

\renewenvironment{rSection}[1]{
  \sectionskip
  {\color{headerblue}\textbf{\MakeUppercase{#1}}}
  \sectionlineskip
  {\color{rulegray}\hrule height 0.6pt}
  \vspace{0pt}
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}
  }
  \item[]
}{
  \end{list}
}

\name{Pham Hung Quoc Viet}
\address{+84 937 404 708 \\ Thu Duc, Ho Chi Minh City \\ \href{mailto:phamviet1415@gmail.com}{phamviet1415@gmail.com} \\ \href{https://github.com/vietpham10205}{github.com/vietpham10205}}

\begin{document}

\begin{rSection}{Objective}
\vspace{-2pt}
{Proactive 3rd-year Information Systems student at University of Information Technology -- VNU-HCM (UIT) with a strong foundation in Business Analysis, Data Warehousing, and Process Optimization. Experienced in requirements analysis, system modeling, and translating complex data/AI capabilities into actionable business values. Seeking a \textbf{Business Analyst Intern} position to leverage my technical background (ERP, BI, AI/ML) and analytical mindset to support ERP/AI ERP implementation, streamline business processes, facilitate UAT, and deliver high-quality user experiences.}
\end{rSection}

\begin{rSection}{Education}
\vspace{-2pt}
University of Information Technology -- VNU-HCM (UIT) \hfill 2023 -- 2027 (expected)\\
\textbf{Bachelor of Information Systems} \hfill GPA: 8.06/10 \\
\textit{Relevant Coursework: Information Systems Analysis \& Design, Database Management Systems, Data Mining, Web Development}
\end{rSection}

\begin{rSection}{Skills}
\vspace{-2pt}
    \renewcommand{\arraystretch}{0.95}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{2.5ex}} >{\raggedright\arraybackslash}p{5.4in} @{} }
        Business Analysis     & Requirement Gathering, Process Mapping, Documentation, UAT Support, Stakeholder Communication \\
        ERP \& Systems        & SAP S/4HANA, Odoo, Data Warehousing (SSIS, SSAS), System Integration \\
        Tools \& Management   & draw.io, UML, Figma, Notion, Agile/Scrum Methodology, Excel/Google Sheets, PowerPoint \\
        Data Analysis \& BI   & Power BI, Advanced Excel (Pivot, Power Query), SQL (SQL Server, PostgreSQL, MySQL), MDX \\
        AI \& Tech Background & Python (Pandas, Scikit-learn), AI/ML (Predictive Modeling, Anomaly Detection), Apache Spark, Kafka \\
        Languages \& Others   & IELTS 6.5 (2022), Logical Thinking, Problem Solving \\
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
\end{rSection}

\begin{rSection}{Projects}
    \item \textbf{E-commerce Consumer Behaviour Analysis \& BI Solution} \hfill 2025\\
    {\small \textit{SSIS, SSAS, SQL Server, Power BI, MDX, Python, Scikit-learn}} \hfill | \href{https://github.com/vietpham10205/Datawarehouse-Olap_Project-E-commerce-Consumer-Behavior-Analysis-BI-Solution}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{Requirements \& Process Mapping:} Analyzed business requirements for e-commerce performance tracking; mapped data flows to design a Star Schema and OLAP cubes for multi-dimensional cohort analysis.
        \item \textbf{ETL \& System Architecture:} Built automated SSIS pipelines to clean and centralize 100k+ transaction records into a SQL Server Data Warehouse, ensuring data consistency for downstream reporting.
        \item \textbf{Data Mining \& Insights:} Applied K-Means clustering and Decision Trees to perform customer segmentation and predict spending levels, delivering actionable insights on customer lifetime value.
        \item \textbf{Reporting \& Documentation:} Developed interactive Power BI dashboards integrating OLAP cubes and ML predictions to monitor retention and purchase frequency; prepared clear metric documentation for end-users.
    \end{itemize}
    }
    \vspace{5pt}

    \item \textbf{Bank Customer Churn Prediction \& Explainability (AI/ML)} \hfill 2026\\
    {\small \textit{Python, Scikit-learn, TensorFlow, XGBoost, LightGBM, SMOTE, SHAP}} \hfill | \href{https://github.com/ThanhThang5722/Bank-Customer-Churn-Prediction}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{Business Problem Solving:} Addressed the critical business issue of customer churn by analyzing a 10k-record European bank dataset to identify core behavioral indicators.
        \item \textbf{Data Analysis \& Preprocessing:} Conducted exploratory data analysis (EDA), handled 80/20 class imbalance with SMOTE, and engineered new features to improve prediction accuracy.
        \item \textbf{Predictive Modeling:} Benchmarked multiple ML algorithms (XGBoost, Random Forest, etc.) to accurately identify users at high risk of churning.
        \item \textbf{Insights \& Explainability:} Utilized SHAP and LIME to interpret model results, translating complex AI/ML outputs into understandable business drivers (e.g., active membership, product usage) for stakeholders.
    \end{itemize}
    }
    \vspace{5pt}

    \item \textbf{NYC Taxi — Real-time Fleet Intelligence \& Anomaly Detection} \hfill 2026\\
    {\small \textit{PySpark, Kafka, Docker, PostgreSQL, Streamlit, Pandas, Scikit-learn}} \hfill | \href{https://github.com/vietpham10205/real-time-Fleet-Intelligence-anomaly-detection-dashboard}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{System Design \& Implementation:} Designed the architecture for a real-time fleet monitoring system using PySpark and Kafka to process JSON events at 200 msg/s.
        \item \textbf{Risk Management \& AI:} Deployed an Isolation Forest + MinCovDet ensemble model to detect real-time route anomalies, enhancing operational risk control and automation.
        \item \textbf{UI/UX \& User Feedback:} Built an interactive Streamlit dashboard for real-time operational reporting, ensuring smooth user experience for system managers and facilitating easy performance tracking.
        \item \textbf{Testing \& Reliability:} Conducted continuous system testing, monitored data streams into PostgreSQL, and automated model retraining to maintain high system reliability.
    \end{itemize}
    }
\end{rSection}

\end{document}
