\documentclass{resume}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.35in,top=0.20in,right=0.35in,bottom=0.15in]{geometry}
\usepackage{setspace}
\setstretch{0.92}
\emergencystretch=2em
\usepackage{enumitem}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% Redefine section and name spacing for single-page layout
\renewcommand{\sectionskip}{\vspace{2.5pt}}
\renewcommand{\sectionlineskip}{\vspace{1pt}}
\renewcommand{\nameskip}{\vspace{1pt}}
\renewcommand{\addressskip}{\vspace{1pt}}

\renewenvironment{rSection}[1]{
  \sectionskip
  {\color{headerblue}\textbf{\MakeUppercase{#1}}}
  \sectionlineskip
  {\color{rulegray}\hrule height 0.6pt}
  \vspace{0pt}
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}
  }
  \item[]
}{
  \end{list}
}

\name{Pham Hung Quoc Viet}
\address{+84 937 404 708 \\ Thu Duc, Ho Chi Minh City \\ \href{mailto:phamviet1415@gmail.com}{phamviet1415@gmail.com} \\ \href{https://github.com/vietpham10205}{github.com/vietpham10205}}

\begin{document}

\begin{rSection}{Objective}
\vspace{-2pt}
{Proactive 3rd-year Information Systems student at University of Information Technology -- VNU-HCM (UIT) with a passion for web development and crafting engaging user interfaces. Aspiring to become a Software Engineer with a focus on Frontend Development. Adept at problem-solving, responsive design, and translating complex data into intuitive interactive dashboards. Seeking the \textbf{Product Frontend Intern} position at Geek Internship Autumn 2026 to leverage my analytical skills, learn modern frontend technologies, and contribute to real-world product development in a collaborative team environment. Available full-time from 17/08/2026 to 23/10/2026.}
\end{rSection}

\begin{rSection}{Education}
\vspace{-2pt}
University of Information Technology -- VNU-HCM (UIT) \hfill 2023 -- 2027 (expected)\\
\textbf{Bachelor of Information Systems} \hfill GPA: 8.06/10 \\
\textit{Relevant Coursework: Web Development, Information Systems Analysis \& Design, Database Management Systems, Data Mining}
\end{rSection}

\begin{rSection}{Skills}
\vspace{-2pt}
    \renewcommand{\arraystretch}{0.95}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{2.5ex}} >{\raggedright\arraybackslash}p{5.4in} @{} }
        Frontend \& Web Dev   & JavaScript, HTML5, CSS3, Responsive Web Design, UI/UX Implementation, DOM Manipulation \\
        UI/UX \& Tools        & Figma, Streamlit, Git, GitHub, Docker, draw.io, UML \\
        Programming           & Python, Java, C++, SQL, RESTful API Concepts \\
        Data Visualization    & Power BI, Plotly, Seaborn, Matplotlib, Interactive Dashboards \\
        Core Competencies     & Problem Solving, Agile/Scrum Methodology, Cross-Functional Collaboration, Testing \& Debugging \\
        Languages \& Others   & IELTS 6.5 (2022), Proactive Learning, Analytical Thinking \\
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
\end{rSection}

\begin{rSection}{Projects}
    \item \textbf{NYC Taxi — Real-time Fleet Intelligence Web Dashboard} \hfill 2026\\
    {\small \textit{Streamlit, Python, PySpark, PostgreSQL, Kafka}} \hfill | \href{https://github.com/vietpham10205/real-time-Fleet-Intelligence-anomaly-detection-dashboard}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{Frontend UI Implementation:} Designed and developed an interactive Streamlit web dashboard to visualize real-time fleet operations and anomaly detection results, focusing on a clean layout and seamless user experience.
        \item \textbf{Data Integration \& Responsiveness:} Connected the frontend interface with PostgreSQL and streaming data to dynamically update maps and statistical charts without page reloads, ensuring high responsiveness.
        \item \textbf{User-Centric Design:} Prioritized UI/UX by providing intuitive filtering controls and visual alerts for system managers to monitor anomalies and track performance efficiently.
        \item \textbf{Testing \& Debugging:} Conducted continuous testing of the UI components and data pipelines to ensure stability, optimal rendering speed, and cross-platform compatibility of the dashboard.
    \end{itemize}
    }
    \vspace{5pt}

    \item \textbf{E-commerce Consumer Behaviour Interactive Dashboard} \hfill 2025\\
    {\small \textit{Power BI, SQL Server, Python, SSIS, SSAS}} \hfill | \href{https://github.com/vietpham10205/Datawarehouse-Olap_Project-E-commerce-Consumer-Behavior-Analysis-BI-Solution}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{UI Design \& Visualization:} Translated complex customer segmentation and predictive ML outputs into engaging, easy-to-understand visual interfaces using Power BI.
        \item \textbf{Requirement Analysis:} Collaborated with stakeholders to understand business goals and mapped data flows to design intuitive dashboard layouts that directly addressed user needs.
        \item \textbf{Performance Optimization:} Optimized data queries, indexing, and rendering processes to ensure the dashboard loaded quickly and smoothly when handling over 100,000 transaction records.
        \item \textbf{Documentation \& Collaboration:} Maintained clear documentation for the dashboard's interactive features and metrics, facilitating easy adoption and effective communication with non-technical team members.
    \end{itemize}
    }
    \vspace{5pt}

    \item \textbf{Bank Customer Churn Analysis \& Explainability} \hfill 2026\\
    {\small \textit{Python, Scikit-learn, Pandas, SHAP, LIME}} \hfill | \href{https://github.com/ThanhThang5722/Bank-Customer-Churn-Prediction}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{Data Presentation:} Developed clear visualizations and explainability reports (using SHAP and LIME) to interpret complex AI/ML outputs, effectively translating them into understandable visual drivers for business users.
        \item \textbf{Analytical Problem Solving:} Applied strong analytical skills to meticulously clean, normalize, and extract actionable features from a 10,000-record dataset, demonstrating a keen eye for detail.
        \item \textbf{Team Collaboration:} Worked closely in a collaborative environment to research algorithms, maintaining a clean, version-controlled codebase using Git/GitHub for seamless team integration.
    \end{itemize}
    }
\end{rSection}

\end{document}
