\documentclass{resume}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.35in,top=0.20in,right=0.35in,bottom=0.15in]{geometry}
\usepackage{setspace}
\setstretch{1.05}
\emergencystretch=2em
\usepackage{enumitem}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% Redefine section and name spacing for single-page layout
\renewcommand{\sectionskip}{\vspace{5pt}}
\renewcommand{\sectionlineskip}{\vspace{3pt}}
\renewcommand{\nameskip}{\vspace{3pt}}
\renewcommand{\addressskip}{\vspace{3pt}}

\renewenvironment{rSection}[1]{
  \sectionskip
  {\color{headerblue}\textbf{\MakeUppercase{#1}}}
  \sectionlineskip
  {\color{rulegray}\hrule height 0.6pt}
  \vspace{0pt}
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}
  }
  \item[]
}{
  \end{list}
}

\name{Pham Hung Quoc Viet}
\address{+84 937 404 708 \\ Thu Duc, Ho Chi Minh City \\ \href{mailto:phamviet1415@gmail.com}{phamviet1415@gmail.com} \\ \href{https://github.com/vietpham10205}{github.com/vietpham10205}}

\begin{document}

\begin{rSection}{Objective}
\vspace{-2pt}
{3rd-year Information Systems student at University of Information Technology -- VNU-HCM (UIT) with a strong foundation in Business Analysis, Data Warehousing, and Process Optimization. Experienced in requirements gathering, system modeling, and translating complex data into actionable dashboards. Seeking an \textbf{ERP Intern} position to leverage analytical skills and technical background to support smart factory solutions (MES/ERP/IoT), streamline business processes, and facilitate UAT.}
\end{rSection}

\begin{rSection}{Education}
\vspace{-2pt}
University of Information Technology -- VNU-HCM (UIT) \hfill 2023 -- 2027 (expected)\\
\textbf{Bachelor of Information Systems} \hfill GPA: 8.06/10 \\
\textit{Relevant Coursework: Information Systems Analysis \& Design, Database Management Systems, Data Mining, Web Development}
\end{rSection}

\begin{rSection}{Skills}
\vspace{-2pt}
    \renewcommand{\arraystretch}{0.95}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{2.5ex}} >{\raggedright\arraybackslash}p{5.4in} @{} }
        Business Analysis     & Requirement Gathering, Process Modeling (Draw.io, Visio), BRD, User Stories, UAT \\
        Data \& ERP           & Data Warehousing, Data Analysis, Power BI, SSIS, SSAS, Microsoft Office \\
        Design \& Tools       & Figma, Axure, Jira, Git/GitHub, Docker, Streamlit \\
        Programming           & SQL, Python, HTML, CSS, Java, C++, PHP \\
        Languages             & IELTS 6.5 (2022) \\
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
\end{rSection}

\begin{rSection}{Projects}
    \item \textbf{E-commerce Consumer Behaviour Analysis \& BI Solution} \hfill 2025\\
    {\small \textit{SSIS, SSAS, SQL Server, Power BI, Python, Draw.io, Visio}} \hfill | \href{https://github.com/vietpham10205/Datawarehouse-Olap_Project-E-commerce-Consumer-Behavior-Analysis-BI-Solution}{GitHub}
    {\small
    \begin{itemize}[itemsep=4pt, parsep=0pt, leftmargin=1.2em]
        \item \textbf{Business Requirement Analysis (BRD):} Collected and analyzed reporting requirements from various departments; authored Business Requirement Documents (BRD) and user stories to align technical deliverables with business goals.
        \item \textbf{Process Modeling \& Data Warehousing:} Modeled data flow processes using Draw.io and Visio; designed a Star Schema architecture and built SSAS cubes to centralize 100k+ transaction records.
        \item \textbf{Data Analysis \& Visualization:} Developed interactive Power BI dashboards utilizing SQL and MDX to visualize customer segmentation KPIs, providing actionable insights for stakeholders.
        \item \textbf{System Testing (UAT) \& Documentation:} Conducted rigorous software testing and facilitated User Acceptance Testing (UAT) with end-users, delivering comprehensive documentation to ensure smooth adoption.
    \end{itemize}
    }
    \vspace{15pt}

    \item \textbf{NYC Taxi — Real-time Fleet Monitoring System (IoT/Smart Factory Concept)} \hfill 2026\\
    {\small \textit{PySpark, Kafka, PostgreSQL, Streamlit, HTML/CSS, Docker, Figma, Axure}} \hfill | \href{https://github.com/vietpham10205/real-time-Fleet-Intelligence-anomaly-detection-dashboard}{GitHub}
    {\small
    \begin{itemize}[itemsep=4pt, parsep=0pt, leftmargin=1.2em]
        \item \textbf{System Architecture \& Wireframing:} Researched Smart Factory (IoT/MES) concepts to design system workflows; utilized Figma and Axure to create intuitive UI wireframes for a real-time monitoring dashboard.
        \item \textbf{Real-time Data Processing:} Configured a Kafka pipeline to ingest continuous JSON event streams at 200 msg/s, simulating the high-velocity data collection required in modern Manufacturing Execution Systems (MES).
        \item \textbf{Data Analysis \& Anomaly Detection:} Implemented real-time analytical models (Isolation Forest) in Python to monitor route anomalies, translating complex data into operational risk control alerts.
        \item \textbf{Interactive Web UI Deployment:} Built a responsive web dashboard using Streamlit (with custom HTML/CSS) to display live metrics, integrating continuous testing to ensure system reliability and seamless user experience.
    \end{itemize}
    }
\end{rSection}

\end{document}

