\documentclass{resume}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.35in,top=0.20in,right=0.35in,bottom=0.15in]{geometry}
\usepackage{setspace}
\setstretch{0.96}
\emergencystretch=2em
\usepackage{enumitem}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% Redefine section and name spacing for single-page layout
\renewcommand{\sectionskip}{\vspace{2.5pt}}
\renewcommand{\sectionlineskip}{\vspace{1pt}}
\renewcommand{\nameskip}{\vspace{1pt}}
\renewcommand{\addressskip}{\vspace{1pt}}

\renewenvironment{rSection}[1]{
  \sectionskip
  {\color{headerblue}\textbf{\MakeUppercase{#1}}}
  \sectionlineskip
  {\color{rulegray}\hrule height 0.6pt}
  \vspace{0pt}
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}
  }
  \item[]
}{
  \end{list}
}

\name{Pham Hung Quoc Viet}
\address{+84 937 404 708 \\ Thu Duc, Ho Chi Minh City \\ \href{mailto:phamviet1415@gmail.com}{phamviet1415@gmail.com} \\ \href{https://github.com/vietpham10205}{github.com/vietpham10205}}

\begin{document}

\begin{rSection}{Objective}
\vspace{-2pt}
{Analytical 3rd-year student at University of Information Technology -- VNU-HCM (UIT) with a solid foundation in Probability \& Statistics, Time-Series Analysis, and Machine Learning. Experienced in building high-throughput stream processing pipelines, engineering rolling-window statistical features, and benchmarking predictive models using Python and PySpark. Seeking a Quantitative Trading / Fintech Intern position to apply mathematical, statistical, and algorithmic modeling to develop, backtest, and optimize data-driven trading strategies.}
\end{rSection}

\begin{rSection}{Education}
\vspace{-2pt}
University of Information Technology -- VNU-HCM (UIT) \hfill 2023 -- 2027 (expected)\\
\textbf{Bachelor of Information Systems} \hfill GPA: 8.06/10 \\
\textit{Relevant Coursework: Probability \& Statistics, Applied Statistics, Machine Learning, Data Mining, Database Management Systems}
\end{rSection}

\begin{rSection}{Skills}
\vspace{-2pt}
    \renewcommand{\arraystretch}{0.95}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{2.5ex}} >{\raggedright\arraybackslash}p{5.4in} @{} }
        Programming           & Python, SQL, C++, Java, PHP \\
        Quantitative \& Stats  & Probability \& Statistics, Time-Series Analysis, Statistical Modeling, EDA, Data Wrangling \\
        AI \& Machine Learning& Scikit-learn, XGBoost, LightGBM, Random Forest, Anomaly Detection, Feature Engineering, SMOTE, SHAP, Optuna Tuning, TensorFlow \\
        Data \& Big Data       & Pandas, NumPy, Matplotlib, Seaborn, Apache Spark (PySpark), Kafka, SQL Server, PostgreSQL \\
        Tools \& Platforms    & Git, GitHub, Docker, Streamlit, Jupyter Notebook, VS Code, Excel, SSIS \\
        Others \& Languages   & IELTS 6.5 (2022), Agile/Scrum Methodology \\
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
\end{rSection}

\begin{rSection}{Projects}
    \item \textbf{NYC Taxi — Real-time Fleet Intelligence \& Anomaly Detection} \hfill 2026\\
    {\small \textit{PySpark, Kafka, Docker, PostgreSQL, Streamlit, Pandas, Scikit-learn}} \hfill | \href{https://github.com/vietpham10205/real-time-Fleet-Intelligence-anomaly-detection-dashboard}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{Data Ingestion:} Developed low-latency Kafka ingestion pipeline; simulated high-frequency event producer streaming message streams at 200\,msg/s.
        \item \textbf{Time-Series Feature Engineering:} Utilized PySpark Structured Streaming (5,000 offsets/trigger) to compute 14 rolling-window statistical features and moving averages using Pandas.
        \item \textbf{Anomaly \& Pattern Detection:} Designed an Isolation Forest and Minimum Covariance Determinant (MinCovDet) ensemble with strict voting to identify statistical anomalies and regime shifts.
        \item \textbf{Deployment \& Retraining:} Managed continuous ingestion to PostgreSQL; implemented automated model evaluation and parameter retraining triggered every 25 streaming batches.
    \end{itemize}
    }
    \vspace{5pt}

    \item \textbf{Bank Customer Churn Prediction \& Explainability} \hfill 2026\\
    {\small \textit{Python, Scikit-learn, TensorFlow, XGBoost, LightGBM, SMOTE, SHAP, Optuna, Pandas, Seaborn}} \hfill | \href{https://github.com/ThanhThang5722/Bank-Customer-Churn-Prediction}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{Statistical Preprocessing:} Conducted extensive exploratory analysis on a bank dataset; applied Winsorization (outlier mitigation), encoding, and normalization to improve the signal-to-noise ratio.
        \item \textbf{Class Balancing:} Implemented SMOTE to resolve class imbalance (20.4\% positive rate), statistically augmenting data from 6,400 to 10,192 samples to enhance model sensitivity.
        \item \textbf{Predictive Model Benchmarking:} Trained, optimized, and evaluated 7+ machine learning algorithms (XGBoost, Random Forest, LightGBM, etc.) using Optuna and GridSearchCV for hyperparameter tuning.
        \item \textbf{Model Explainability \& Risk Attribution:} Utilized SHAP and LIME to dissect feature contributions; employed Jaccard similarity analysis to quantify stability of key explanatory variables.
    \end{itemize}
    }
    \vspace{5pt}

    \item \textbf{E-commerce Consumer Behaviour Analysis \& BI Solution} \hfill 2025\\
    {\small \textit{SSIS, SSAS, SQL Server, Power BI, MDX, Python, Scikit-learn}} \hfill | \href{https://github.com/vietpham10205/Datawarehouse-Olap_Project-E-commerce-Consumer-Behavior-Analysis-BI-Solution}{GitHub}
    {\small
    \begin{itemize}[nosep, leftmargin=1.2em]
        \item \textbf{Data Pipeline:} Engineered automated SSIS pipelines to clean, pre-process, and consolidate high-volume data streams into SQL Server.
        \item \textbf{Dimensional \& Statistical Modeling:} Modeled a structured Star Schema and built OLAP cubes with MDX to perform hierarchical slice-and-dice data analysis.
        \item \textbf{Quantitative Segmentation:} Implemented K-Means clustering for behavioral segmentation and Decision Tree classification to predict customer spending levels using Python (Scikit-learn).
        \item \textbf{BI Visualization:} Designed interactive dashboards combining model predictions and business metrics to track key performance indicators.
    \end{itemize}
    }
\end{rSection}

\end{document}
